\thesistitle

### 2019-07-25 sections/research.tex
2R thresholds fixed formula

\begin{eqfloat}\label{eq:type2r}
\text{T2R Variability}=\frac{\text{Different expressions}}{\text{Total expressions}}*100
\caption{Type 2R variability threshold formula}\end{eqfloat}

In this formula, \textit{different expressions} refers to the number of literals, variables and method calls that differ from other clone instances in a clone class. We divide this by the total number of expressions in the clone instance. Based on this threshold, we decide whether a clone should be considered for refactoring. A concrete example of applying this formula to calculate a threshold is given in \ref{sec:t2rcheckglobalthres}.

>>>>

\begin{equation}\label{eq:type2r}
\text{T2R Variability}=\frac{\text{Number of different expressions}}{\text{Total number of expressions in clone instance}}*100
\end{equation}

In this formula, \textit{number of different expressions} refers to the number of literals, variables and method calls that differ from other clone instances in a clone class. We divide this by the total number of expressions in the clone instance. Based on this threshold, we decide whether a clone should be considered for refactoring. A concrete example of applying this formula to calculate a threshold is given in \ref{sec:t2rcheckglobalthres}.
